Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-12 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.        
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame16 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Combining Logics}

\begin{frame}{A schematic view of our approach}

\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=1.05 \columnwidth]{figures/figure9.png}
%%\includegraphics[scale=0.5]{figure1}
%\caption{Our approach} %\label{figure9}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Combining Logics}
Given \textbf{two logics} $L_1$ and $L_2$, their \textbf{languages} $\mathcal{L}_1$ and $\mathcal{L}_2$, and their
\textbf{axiomatic systems} $\mathcal{X}_1$ and $\mathcal{X}_2$, the logic
$L_1 \otimes L_2$ is the smallest logic with the following
characteristics:
\begin{itemize}
  \item The language $\mathcal{L}_{L_1\otimes L_2}$ is the union of $\mathcal{L}_{L_1}$ and $\mathcal{L}_{L_2}$.
  \item The logic $L_1 \otimes L_2$ is axiomatised by the set of axioms $\mathcal{X}_1 \cup \mathcal{X}_2$.
\end{itemize}
If the logics $L_1$ and $L_2$ are interpreted using Kripke frames
$F_1 = (S, R_1^1, \dots, R_n^1)$ and $F_2 = (S, R_1^2, \dots
,R_m^2 )$ where $R^1_{x/x\in[1,n]}$ and $R^2_{y/y\in[1,m]}$ are
\textbf{accessibility relations}, then the semantics for $L_1 \otimes L_2$
can be defined in the Kripke frame $F =(S, R_1^1, \dots , R_n^1,
R_1^2, \dots ,R_m^2 )$ obtained by the \textit{independent join} of the two
frames $F_1$ and $F_2$.
    \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame17 Proposed Research
\begin{frame} {Model of CTLKC}
\begin{definition} [Model of CTLKC]\label{Model of CTLKC}
A model $\mathcal{M}=(S,I,R_t,\{\approx_i|i\in \mathcal{ A}\},\{\sim _{i \rightarrow j}|{(i,j)\in \mathcal{A}^2}\},\mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
\begin {itemize}
\item $S, I, R_t$ and $\mathcal{V}$ are the same as in Definition (Model of CTLK);
\item For each agent $i \in \mathcal{A}$, $ \approx _i  \subseteq S \times S
$ is the epistemic accessibility relation defined by $ s \approx_i
s' $ iff $ l_i(s) = l_i(s') $;
\item For each pair $(i, j) \in \mathcal{A}^2 $, $\sim _{i \rightarrow j} \subseteq S \times S $ is the social accessibility relation defined by $ s \sim _{i \rightarrow j} s' $ iff
     1) $ l_i(s) = l_i(s') $ and
     2) $ Var_i \cap Var_j \neq \emptyset $ such that  $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_j^x(s') $ and $ \forall y \in Var_j - Var_i $ we have $ l_j^y(s) = l_j^y(s')$;
\item $ \mathcal{V} : S \rightarrow 2 ^{\Phi_p} $ is a valuation function where $\Phi_p $ is a set of atomic propositions.
\end {itemize}
\label {dfn: Model of CTLKC}
\end{definition}
 \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Syntax of CTLKC}

\begin{definition}[Syntax of CTLKC]~\\
$ ~~~~~~~~~~~~~\varphi ::= p \mid \neg \varphi \mid \varphi \vee
\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
\varphi\mid K_i \varphi \mid C_{i\rightarrow j} \varphi \mid Fu
(C_{i\rightarrow j}\varphi)$. \label {dfn: Syntax of CTLKC}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame18 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Selection Criteria}
We propose the following criteria based on \textbf{common intuitions}:
\begin{itemize}
%\begin{enumerate}
  \item It should not be the case that an agent commits about everything he knows to others.
  \item It should not be the case that an agent commits about everything known by others.
  \item An agent should know about his own commitment.
  \item An agent should be aware of any commitment directed towards him.
  \item An agent should know the content of his fulfilled commitment.
  \item An agent should know the content of any fulfilled commitment directed towards him.

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Continue: Selection Criteria}
\begin{itemize}
 \item An agent should know about the fulfillment of his commitment.
 \item An agent should know about the fulfillment of any commitment directed towards him.
  \item A sincere agent should know (i.e., believe) the content of his own commitment.
  \item A sincere agent should fulfill his commitment.
  \item A liar agent could not know (i.e., believe) the content of his commitment.
  \item If an agent knows about his own commitment, then this commitment should exist, which means an agent should not know about a non-existing commitment.
\end{itemize}
%\end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Running Example: NetBill Payment Protocol}
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=.75 \columnwidth]{figures/figure1.png}
%%\includegraphics[scale=0.5]{figure1}
%\caption{The NetBill payment protocol} \label{figure1}
\end{figure}
\begin{itemize}
\item $C_{Cus \rightarrow Mer}$ $sendPayment$.
 \item $C_{Mer \rightarrow Cus}$ $deliverGoods$.
 \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Desiderata of Paradoxes}

\begin{frame}{Desiderata of Paradoxes}
Paradoxes are represented as reasoning rules that are: 1) not reasonable in
open MAS, but they are valid in CTLKC; or 2) desirable for the
interaction between knowledge and commitments, but they can get
violated in CTLKC because they are not valid.
 \begin{enumerate}

\vspace{0.2cm} \item [P1.]\textbf{[Committing everything known to
others]}

$K_i \varphi \Rightarrow C_{i \rightarrow j}\varphi, $ for all $j
\in A$ where $i \neq j$.

\textbf{ Meaning:} An agent (the debtor) commits towards all other
agents (the creditors) about what he knows.\\
\textbf{Example 1:}
$K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Mer \rightarrow
Cus}$ $deliverGoods$.

\vspace{0.2cm} \item [P2.]\textbf{[Committing everything known by
others]}

 $ K_i K_j \varphi \Rightarrow C_{i \rightarrow j} \varphi$ such that $ i \neq j$.

\textbf{Meaning:} An agent (the debtor) commits toward another
agent (the creditor) to bring about what he (i.e., the debtor)
knows about the creditor's knowledge.\\
\textbf{Example 2:}
$K_{Cus} K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Cus \rightarrow Mer}$
$deliverGoods$.

\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame20 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research Activities Goal}
    \begin{frame}{Research Activities Goal}
    We aim to cover all possible relations between knowledge and commitments as single and group interactions by:

        \begin{itemize}
              \item Defining a new consistent logic that combines knowledge and commitments and solves the nine paradoxes while satisfying the six properties.
              \item Addressing the model checking problem of the new logic from both algorithmic and complexity perspectives.
              \item Implementing the new model checking algorithms on top of MCMAS+.
              \item Identifying a new semantics for group committing.
              \item Adding the group knowledge to the framework.
        \end{itemize}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=.65 \columnwidth]{figures/figure6.png}
%\includegraphics[width=16cm, height=21cm]{figures/figure6.eps}
%\caption{Schedule time of research} \label{figure6}
\end{center}
\end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame27 Milestones %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Publications}

1- Submitted a journal paper entitled ``\textbf{Interaction between knowledge and Social Commitments in MASs}", Applied Intelligence Journal, Springer.\\

>>>>

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty       
        \item (To add some items)
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Coalition Structures}
    \begin{itemize}
        \item To reach a stable partition having many coalitions. 
        \item (To add some items)       
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame16 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Problem Formulation and Modeling}

\begin{frame}{Problem Formulation and Modeling}
    \begin{itemize}
        \item Communities are robust service providers with well established market share and reputation
        \item The community is characterized by a request rate $R_C$
        \item Web services can perform tasks with some throughput rate ($Th_{ws}$)
        \item Web services come with different values of $QoS_{ws}$ for different metrics.
        \item 123
    \end{itemize}    
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Task distribution}
    \begin{itemize}
        \item Our model uses a slightly modified $weighted fair queuing$ method for task distribution rather than Contract-Net.
        \item All the input flow is multiplexed amount different web services with weights proportional to their throughput value ($Th_{ws}$).
        \item Queues will happen if $R_C$ is more than summation web services throughput.
        \item Weighted task rate of: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}    
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community Revenue}
    \begin{itemize}
        \item Maximum potential output of a community:
            \begin{equation*}
                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
            \end{equation*}
        \item if $Th_{ws} > R_C$, the community cannot perform at its maximum potential.
        \item Actual output:
            \begin{equation}\label{out_c}
                Out(C) = \left\{
                  \begin{array}{l l}
                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
                  \end{array} \right.
            \end{equation}
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 1}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_1}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
    \hline
    1 & 0.8 & 4 & 3.2\\
    2 & 0.8 & 5 & 4.0\\
    3 & 0.8 & 3 & 2.4\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_1_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
    $\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
    $\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
    $\left\{1,2,3\right\}$ & 8.0\\
    \hline
    Community $R_C$: 10\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 2}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_2}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
    \hline
    1 & 0.8 & 5 & 4.0\\
    2 & 0.7 & 6 & 4.2\\
    3 & 0.7 & 4 & 2.8\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_2_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
    $\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
    $\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
    $\left\{1,2,3\right\}$ & 7.3\\
    \hline
    Community $R_C$: 10\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 3}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{0.8}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_3}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
    \hline
    1 & 0.8 & 10 & 5\\
    2 & 0.8 & 20 & 5\\
    3 & 0.8 & 30 & 5\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{0.8}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_3_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
    $\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
    $\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
    $\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
    $\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
    $\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
    $\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
    \hline
    Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Web Service Cooperative Games}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Scenario One: Web Services and One Community}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

    \begin{itemize}
        \item A typical WS community, where web services can join or leave
        \item $v(C) = out(C)$
        \item Membership decision in made based on throughput and QoS of the web services.
        \item Community master needs to get quality web services to keep community stable, so other web services have no incentive to leave.

@@

\begin{frame}{Scenario One: Web Services and One Community}
    \begin{itemize}
        \item 123123
        \item 123123
        \item 123123
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research Activities Goal}
\begin{frame}{Research Activities Goal}
    \begin{itemize}
        \item Analyzing other cooperative solution concepts such as Kernel
        and Nucleolus where payoff division is guaranteed to exist and may
        have optimal results.

        \item Applying other valuation function in our scenarios using for
        instance Weighted Voting Games (WCG) in order to develop a
        multiple weighted algorithm to find best coalition structures
        satisfying different weights on each community.

        \item Analyzing the impact of Q-learning and reinforcement
        learning on the performance of our model.

        \item Developing an approximation algorithm for shapely value
        payoff distribution vector in community setting.

        \item Developing a community membership algorithm technique for
        our agents in "incomplete information" settings.

        %\item Developing an open source, Java based Tool, with UI for
        %solving Core and Shapely solution concepts based on different
        %input valuation functions.
    \end{itemize}
\end{frame}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1 \columnwidth]{figures/timetable.png}
%\includegraphics[width=16cm, height=21cm]{figures/figure6.eps}
%\caption{Schedule time of research} \label{figure6}
\end{center}
\end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame27 Milestones %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Publications}

    \begin{enumerate}
        \item Published a paper in 10th International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"} {\color{blue} (Accepted)}
        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing {\color{blue} (Second round of review)}
        \item Submitted a Paper to the 10th International Conference on Service Oriented Computing (ICSOC 2012); \emph{"Analyzing Coopetition Strategies of Services within Communities"} {\color{blue} (Accepted)}
        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing; \emph{"To Compete or to Cooperate? This is the Question in Communities of Autonomous Services"}
    \end{enumerate}
